Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved by tbm, bar size bar plot added

\subsection{EchoNest API}
We use the Echo Nest analyze API \cite{EchoNest} throughout this work.
The API gives us a chroma vector (length $12$) for every music event, 
or ``segment'', for any song we upload to their platform. 
We also get an estimate of where the beats and the bars are. Beats span over
multiple segments, and bars span over multiple beats. 
We transform the chroma vectors per segment into per beat vectors using a 
simple average. We can then stack beat vectors for a number of bars 
(usually 1 or 2). 
We get a fixed-size patch by resampling the number of chroma vectors. Typically,
there are $4$ beats per bar. Thus an appropriate pattern size for one bar
is $12$x$4$ or $12$x$8$.

@@

\section{Visualization} \label{sec:visu}
The goal here is to give an intuition to the reader of what kind of
typical patterns do we get. We also want to have a feel for what the
clusters look like, how many boring sustaned notes are encoded in the
codebook, can the codebook describes the complexity of the music space, etc.

Below we present some figures to help the reader with those questions.
Please keep in mind the limited space.

>>>>

\subsection{EchoNest API}
We use the Echo Nest analyze API \cite{EchoNest} throughout this work.
The API gives us a chroma vector (length $12$) for every music event, 
or ``segment'', for any song we upload to their platform. 
We also get an estimate of where the beats and the bars are. Beats span over
multiple segments, and bars span over multiple beats. 
We transform the chroma vectors per segment into per beat vectors using a 
simple average. We can then stack beat vectors for a number of bars 
(usually 1 or 2). 
We get a fixed-size patch by resampling the number of chroma vectors. Typically,
there are $4$ beats per bar (Figure \ref{fig:barsize}. 
Thus an appropriate pattern size for one bar
is $12$x$4$ or $12$x$8$.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{bar_size_freq}
\end{center}
\caption{\small{
Frequency of the different bar size in the training data.
}}
\label{fig:barsize}
\end{figure}

@@

\section{Visualization} \label{sec:visu}
The goal here is to give an intuition to the reader of what kind of
typical patterns do we get. We also want to have a feel for what the
clusters look like, how many boring sustained notes are encoded in the
codebook, can the codebook describes the complexity of the music space, etc.

Below we present some figures to help the reader with those questions.
Please bear in mind the limited space.
